---
title: "Data Products Week 4 Assignment"
author: "SC"
date: "23 January 2018"
output: ioslides_presentation
---

## Run Prediction

- The Shiny app predicts your race pace (seconds or minutes per kilometer) based upon your cadence (strides per minute).
- It is based upon personal Garmin data gathered over the course of a number of years.
- Predictions are based on a linear model of outcome average pace with predictor of average cadence.
- Predictions are averaged across multiple terrains, elevation and weather.
- A future release of this product will enable users to input these other predictors.

## Structure of Data

The data is based upon personal Garmin data gathered over a course of a number of years.  There are many vaiables, but the key ones are:

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

setwd("C:/Users/steve.a.cooper/Google Drive/Coursera - DS/ds_9_dp/ds_9_dp_wk4/CourseProject")
library(shiny)
library(tidyverse)

# import the dataset
runlog <- read_csv("runlog.csv", 
                   col_types = list(AvgPace = col_time(format = "%M:%S")))
runlog$AvgCadence <- as.numeric(runlog$AvgCadence)

str(runlog)
```

```{r str}
str(runlog)
```

## Data Header

Here are the first 5 rows of the data and summary:

```{r head}
head(runlog)
```

## Data Summary

Here are the first 5 rows of the data and summary:

```{r summary}
summary(runlog)
```
